Deep mutational scanning of hemagglutinin helps predict evolutionary fates of human H3N2 influenza variants

### 2018-06-24 paper/manuscript.tex
Added codon details

\begin{suppfigure}[H]
\centerline{\includegraphics[width=0.4\textwidth]{figs/supp_point_mut_validation/glycan_titers.pdf}}
\caption{\label{suppfig:glycan_validation}
{\bf Validation of viral variants with mutations at N-linked glycosylation motifs.}
We created variants of the Perth/2009 HA with mutations that eliminated N-linked glycosylation motifs (Asn-Xaa-Ser/Thr) at asparagine residues 22, 38, and 285 (these are mutations T24F, T40V, and S287A, respectively).
\comment{The codon mutations were NNN$\rightarrow$NNN, NNN$\rightarrow$NNN, and NNN$\rightarrow$NNN, respectively.}
We then used reverse genetics to generate viruses carrying the wildtype HA or each of these mutants.
Each variant was generated in duplicate, and the plots show the viral titer in the supernatant at 53 hours post-transfection.
The viruses with mutations at the motifs at residues 22 and 38 reached titers at least as high as wildtype, whereas the virus with a mutation to the motif at residue 285 was modestly attenuated.
}
\end{suppfigure}

\begin{suppfigure}[H]
\centerline{\includegraphics[width=0.45\textwidth]{figs/supp_point_mut_validation/tm_titers.pdf}}
\caption{\label{suppfig:TM_validation}
{\bf Validation of the mutational tolerance of a site in the transmembrane domain.}
We created a variant of the Perth/2009 HA with a transmembrane domain mutation, C199(HA2)K (\comment{codon mutation NNN$\rightarrow$NNN}), at a site that our deep mutational scanning suggests should be highly mutationally tolerant (Figure~\ref{fig:logoplot}).
We then used reverse genetics to generate viruses carrying the wildtype HA or this mutant.
Each variant was generated in duplicate, and the plots show the viral titer in the supernatant at 53 hours post-transfection.
The virus with the mutation reached titers comparable to wildtype.
}
\end{suppfigure}

>>>>

\begin{suppfigure}[H]
\centerline{\includegraphics[width=0.4\textwidth]{figs/supp_point_mut_validation/glycan_titers.pdf}}
\caption{\label{suppfig:glycan_validation}
{\bf Validation of viral variants with mutations at N-linked glycosylation motifs.}
We created variants of the Perth/2009 HA with mutations that eliminated N-linked glycosylation motifs (Asn-Xaa-Ser/Thr) at asparagine residues 22, 38, and 285 (these are mutations T24F, T40V, and S287A, respectively).
The codon mutations were ACG$\rightarrow$TTC, ACT$\rightarrow$GTA, and AGC$\rightarrow$GCG, respectively.
We then used reverse genetics to generate viruses carrying the wildtype HA or each of these mutants.
Each variant was generated in duplicate, and the plots show the viral titer in the supernatant at 53 hours post-transfection.
The viruses with mutations at the motifs at residues 22 and 38 reached titers at least as high as wildtype, whereas the virus with a mutation to the motif at residue 285 was modestly attenuated.
}
\end{suppfigure}

\begin{suppfigure}[H]
\centerline{\includegraphics[width=0.45\textwidth]{figs/supp_point_mut_validation/tm_titers.pdf}}
\caption{\label{suppfig:TM_validation}
{\bf Validation of the mutational tolerance of a site in the transmembrane domain.}
We created a variant of the Perth/2009 HA with a transmembrane domain mutation, C199(HA2)K (codon mutation TGT$\rightarrow$AAG), at a site that our deep mutational scanning suggests should be highly mutationally tolerant (Figure~\ref{fig:logoplot}).
We then used reverse genetics to generate viruses carrying the wildtype HA or this mutant.
Each variant was generated in duplicate, and the plots show the viral titer in the supernatant at 53 hours post-transfection.
The virus with the mutation reached titers comparable to wildtype.
}
\end{suppfigure}
